Image restoration using dimensionality reduction in the Fourier domain

### 2011-06-08 project/Paper/paper.tex
Small commit so I can switch branches

((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.

>>>>

In our implementation, we use several tweaks to improve performance or quality:
\begin{itemize}
\item We use an extended neighborhood when ((( TODO )))
\end{itemize}

We use a 
((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.
